\begin{abstract}\label{sec:abstract}
  In 2015, ECMAScript 6 (ES6, 2015) introduced a new wave in JavaScript with
  various new language features. It is the start of the fast-evolving nature of
  JavaScript with an annual release cadence and open development process.
  However, most JavaScript engines did not support or partially supported newly
  introduced features in the beginning. Therefore, \textit{transpilers} showed
  up to fulfill developers' desires to use new language features before
  JavaScript engines would support them. They \textit{desugar} such features to
  transpile JavaScript programs from ES6 or later versions to ECMAScript 5 (ES5,
  2009). Even though most engines now support language features even in the
  latest ECMAScript, developers still heavily utilize them to execute their
  JavaScript programs in legacy engines. However, there is no empirical study to
  answer the correctness or quality of their desugaring process even though six
  years have passed since 2015.

  This paper takes the first step to systematically studying the desugaring
  process of Babel, the most dominating JavaScript transpiler. We measure the
  quality of desugaring process from ES6 or later versions to ES5 based on its
  \textit{semantics preservation}, \textit{speed degradation}, and \textit{code
  bloat}. We develop $\tool$, a JavaScript program generator using genetic
  algorithms, to automatically measure the quality and find the worst cases in
  each metric. To evenly treat each language feature under the same granularity,
  we introduce a solid definition of JavaScript language features and an
  automated approach to extract them from JavaScript programs using their
  statistical information. Our experiments show that Babel incorrectly desugars
  \inred{XX} language features, degrades the execution speed by \inred{XX.X}\%
  on average, and bloats code sizes by \inred{XX.X}\% on average. In the worst
  case, the speed was \inred{XX.X} times slower, and the size was \inred{XX.X}
  times increased. We believe that this study provides a foundation for building
  a sound and practical desugaring process in JavaScript transpilers.
\end{abstract}
